---
title: "color_your_ggplot_beautiful_rladies_freeburg"
author: "Onkar Singh"
date: "10/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[youtube link](https://www.youtube.com/watch?v=A4fP31h4roU&t=4189s)


```{r}
library(tidyverse)
library(palmerpenguins)
```


```{r}
penguins <- palmerpenguins::penguins %>% drop_na()
```

## Basic Plots
1. penguins_flipper: scatterplot
```{r}
(penguins_flipper <- ggplot(penguins) + 
  aes(x = flipper_length_mm, y = body_mass_g) +
  geom_point(show.legend = FALSE) + 
  labs(x = "Flipper length", 
       y = "Body mass", 
       title = "Palmer pegnuins flipper length and body mass") +
  theme_minimal())
```

2. penguins_bill: scatterplot with trend line

```{r}
(penguins_bill <- ggplot(penguins) + 
  aes(x = bill_length_mm, y = bill_depth_mm) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  labs( x = "Bill length", 
        y = "Bill depth", 
        title = "Palmer penguins bill length and depth") + 
  theme_minimal())
```

3. penguins_island: bar chart

```{r}

(penguins_island <- penguins %>% 
  filter(island != " Torgersen")%>% # removing this island since it has only one species
  ggplot() + 
  aes(x = island) + 
  geom_bar(position = "dodge") + # This will be helpful later
  labs( x = "Island", 
        y = "n", 
        title = "Palmer penguins by island") + 
  theme_minimal())

  
  ggplot(penguins) +
  aes(x = )
```


## Colors in ggplot 2

- color for small areas like dots and lines
- fill for larger areas

-Mapping to columns that already exists in aes: adds color
- Mapping to colums not yet displayed in the graph: add information/can seemingly change the behavior of geoms

Note that you can add to the aes of the plot that is saved  as a variable

```{r}
(penguins_island  + 
  aes(fill =  island))

(penguins_island + 
    aes(fill = species) + 
    geom_bar(position = "dodge"))
```


```{r}
(penguins_flipper <- penguins_flipper + 
   aes(color = body_mass_g)
 )
```

