---
title: "janitor_tablys"
author: "Onkar Singh"
date: "12/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

see vignette("tabyls") for details


```{r}
library(dplyr)
humans <- starwars %>% 
  filter(species == "Human")

glimpse(humans)
```


# One-way tabyl

Tabulating a single variable is the simplest kind of tabyl

```{r}
library(janitor)

t1 <- humans %>% 
  tabyl(eye_color)
```

When NA values are present, tabyl() also displays “valid” percentages, i.e., with missing values removed from the denominator. And while tabyl() is built to take a data.frame and column names, you can also produce a one-way tabyl by calling it directly on a vector:

```{r}
x <- c("big", "big", "small", "small", "small", NA)
tabyl(x)
```

Most adorn_ helper functions are built for 2-way tabyls, but those that make sense for a 1-way tabyl do work:

```{r}
t1 %>% 
  adorn_totals("row") %>% 
  adorn_pct_formatting()
```

# Two-way tabyl

This is often called a “crosstab” or “contingency” table. Calling tabyl on two columns of a data.frame produces the same result as the common combination of dplyr::count(), followed by tidyr::pivot_wider() to wide form:

```{r}
t2 <- humans %>% 
  tabyl(gender, eye_color)
```


```{r}
humans %>% count(gender, eye_color) %>% 
  tidyr::pivot_wider(names_from = eye_color, values_from = n)
```

Since it’s a tabyl, we can enhance it with adorn_ helper functions. For instance:

```{r}
t2 %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(digts = 2) %>% 
  adorn_ns()
```

Adornments have options to control axes, rounding, and other relevant formatting choices (more on that below).

# Three-way tabyl

Just as table() accepts three variables, so does tabyl(), producing a list of tabyls:

```{r}
t3 <- humans %>%
  tabyl(eye_color, skin_color, gender)

```

If the adorn_ helper functions are called on a list of data.frames - like the output of a three-way tabyl call - they will call purrr::map() to apply themselves to each data.frame in the list:

```{r}
library(purrr)
humans %>%
  tabyl(eye_color, skin_color, gender, show_missing_levels = FALSE) %>%
  adorn_totals("row") %>%
  adorn_percentages("all") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns %>%
  adorn_title
```







