---
title: "Payment Details"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document: default
theme: flatly
toc: yes
toc_float: yes
---

```{r add this yaml for word document print}
# output:
#   word_document: default
#   html_document:
#     code_download: yes
#   pdf_document: default
# theme: flatly
# toc: yes
# toc_float: yes
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE, 
  message = FALSE, 
  echo = FALSE
)

```

```{r}
library(tidyverse)
library(janitor)
library(lubridate)
library(writexl)
library(ggrepel)
```

### Payments/Disbursements

[**gg_payments_scheduled_and_actual report link**](https://impactaccenture.lightning.force.com/lightning/r/Report/00O1I000006ho72UAA/view)

### Step 1: Reading the file

```{r}
# Reading the file
bookroyaltiesgrants <- c("Fundaula Book Royalty Grant", 
                         "FY19 LC Success Coaching - Global", "Human + Machine Book Royalty Grant", "ELBA"
                         )
payments <- read_csv("gg_payments_scheduled_and_actual.csv") %>%
  clean_names() %>% 
  filter(!friendly_name %in% bookroyaltiesgrants)
  

```

### Grant Statuses

```{r}
payments %>% 
  count(grant_status)
```

```{r}
payments <- payments %>% 
  filter(!grant_status %in% c("In Progress", "New"))
```

### Step 2: Data Processing 2

```{r}
# Data Processing Step 1
payments_processed <- payments %>%
  filter(type_of_payment == "Cash") %>%
  mutate(
    scheduled_payment_date = mdy(scheduled_payment_date),
    due_date_month = month(scheduled_payment_date),
    due_date_year = year(scheduled_payment_date),
    adjustment = as.integer(due_date_month >= 9),
    fiscal_year = due_date_year + adjustment
  )
```

### Step 3: Data Processing 3

```{r}
# Data Processing Step 2
payments_processed <- payments_processed %>%
  mutate(fdn_cat = if_else(funding_foundation == "US Foundation", "US Fdn", "Other Fdn")) %>%
  mutate(
    live_pipe = case_when(
      .$grant_status %in% c("New", "In Progress") ~ "Pipeline",
      .$grant_status %in% c("Signed", "Launched", "Ready for Closure") ~ "Live",
      TRUE ~ "Closed"
    )
  ) %>%
  select(
    funding_foundation,
    fdn_cat,
    live_pipe,
    friendly_name,
    grant_status,
    scheduled_payment_date,
    scheduled_amount,
    actual_payment_date,
    actual_amount,
    fiscal_year
  ) 
```

## Live+Closed (to get the full figures we have to filter grant status != Pipe, since we also need figures for closed grants to get the full figure per FY)

### Summary committed and actual per FY/YTD

```{r results = TRUE}

live_plus_pipe_per_fy <- payments_processed %>%
  arrange(scheduled_payment_date) %>%
    group_by(fiscal_year, funding_foundation, friendly_name) %>%
        summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)) 

live_plus_pipe_per_fy%>% 
  DT::datatable(filter = "top", extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download')
      )
  )
  )


# writexl::write_xlsx("Australia_Fdn_FY20-FY22.xlsx")
  
```

### Summary committed and actual Live (+ clsoed if any)) Grants per FY/YTD

```{r,  results = 'asis'}

live_grants_per_fy <- payments_processed %>%
  filter(live_pipe != "Pipe") %>%
  arrange(scheduled_payment_date) %>%
  group_by(fiscal_year) %>%
  summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)
      )
live_grants_per_fy
```

```{r results = TRUE}
# Summary committed and actual Live Grants US Fdn per FY/YTD
live_grants_per_fy_us_fdn <- payments_processed %>%
  filter(live_pipe != "Pipe",
         fdn_cat == "US Fdn") %>%
  arrange(scheduled_payment_date) %>%
  group_by(fiscal_year) %>%
  summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)
  )
live_grants_per_fy_us_fdn
```

### Summary committed and actual Live Grants (+ clsoed if any) Other Fdn per FY/YTD

```{r results = TRUE}

live_grants_per_fy_other_fdn <- payments_processed %>%
  filter(live_pipe != "Pipe",
         fdn_cat == "Other Fdn") %>%
  arrange(scheduled_payment_date) %>%
  group_by(fiscal_year) %>%
  summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)
  )
live_grants_per_fy_other_fdn 
```

### Summary committed and actual Live (+ clsoed if any) Grants per year per Fdn

```{r results = TRUE}

live_grants_per_fy_other_fdn <- payments_processed %>%
  filter(live_pipe != "Pipe") %>%
  arrange(scheduled_payment_date) %>%
  group_by(fiscal_year, fdn_cat) %>%
  summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)
  )
live_grants_per_fy_other_fdn 
 
```

### Summary committed and actual Live(+ clsoed if any) Grants per year per Individual Fdn

```{r ,  results = TRUE}


live_grants_per_fy_other_fdn <- payments_processed %>%
  filter(live_pipe != "Pipe") %>%
  arrange(scheduled_payment_date) %>%
  group_by(fiscal_year, funding_foundation) %>%
  summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)
  )
live_grants_per_fy_other_fdn 
# %>% filter(fiscal_year == 2020) just use this added line in the code chunk above/below to get an FY picture per foundation n basis other groups that follow
 
```

### Summary committed and actual Live (+ clsoed if any) Grants per year per Fdn

```{r results = TRUE}

live_grants_per_fy_other_fdn <- payments_processed %>%
  filter(live_pipe != "Pipe") %>%
  arrange(scheduled_payment_date) %>%
  group_by(fiscal_year, fdn_cat, grant_status, friendly_name) %>%
  summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)
  )
live_grants_per_fy_other_fdn 
```

### Summary committed and actual Live (+ closed if any)Grants per year per Individual Foundation

```{r}

live_grants_per_fy_other_fdn <- payments_processed %>%
  filter(live_pipe != "Pipe") %>%
  arrange(scheduled_payment_date) %>%
  group_by(fiscal_year, funding_foundation, grant_status, friendly_name) %>%
  summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)
  )
live_grants_per_fy_other_fdn 
# %>%  filter(fiscal_year ==2020) use this step for per year picture


##Pipeline starts
### Summary committed  Pipeline Grants per FY/YTD

```

```{r}

pipeline_grants_per_fy <- payments_processed %>%
  filter(live_pipe == "Pipeline") %>%
  arrange(scheduled_payment_date) %>%
  group_by(fiscal_year) %>%
  summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)
  )
pipeline_grants_per_fy %>% 
  knitr::kable()
```

## Pipeline starts here

### Summary committed Pipeline Grants US Fdn per FY/YTD

```{r}

pipeline_grants_per_fy_us_fdn <- payments_processed %>%
  filter(live_pipe == "Pipeline",
         fdn_cat == "US Fdn") %>%
  arrange(scheduled_payment_date) %>%
  group_by(fiscal_year) %>%
  summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)
  )
pipeline_grants_per_fy_us_fdn %>% 
  knitr::kable()
```

### Summary committed Pipeline Grants Other Fdn per FY/YTD

```{r}
pipeline_grants_per_fy_other_fdn <- payments_processed %>%
  filter(live_pipe == "Pipeline",
         fdn_cat == "Other Fdn") %>%
  arrange(scheduled_payment_date) %>%
  group_by(fiscal_year) %>%
  summarize(
    scheduled_totalytd = sum(scheduled_amount, na.rm = T),
    actual_totalytd = sum(actual_amount, na.rm = T)
  )
pipeline_grants_per_fy_other_fdn %>% 
  knitr::kable()
```

### Current FY Payment Details

```{r}

payments_fy21 <- payments_processed %>%
  filter(fiscal_year == 2021)%>%
   filter(!grant_status%in%c("New", "In Progress"), 
         !friendly_name %in% c("Fundaula Book Royalty Grant")) %>% 
  select(
    fiscal_year,
    friendly_name,
    grant_status,
    scheduled_payment_date,
    scheduled_amount,
    actual_payment_date,
    actual_amount
  ) %>%
  arrange(friendly_name) 
payments_fy21 %>% 
   # knitr::kable()
  flextable::flextable() %>% 
  flextable::border_inner() %>% 
  flextable::border_outer() %>% 
  flextable::colformat_num(j = c(5,7), digits = 0) %>% 
  flextable::colformat_num(j = 1, big.mark = "", digits = 0) %>% 
  flextable:: bold(part = "header")
```

### FY21 Scheduled and Actual Amount

```{r}
payments_fy21 %>%
  summarize(across(c(scheduled_amount, actual_amount), sum, na.rm = TRUE))
```

```{r}
# payments_fy21 %>% 
#   write_xlsx("payments_fy21.xlsx")
```

### Graph Current FY Payment

```{r}
payments_processed %>% 
  filter(fiscal_year == 2021) %>% 
  mutate(payment_done = ifelse(actual_amount > 0,  "yes", "no")) %>% 
    ggplot(aes(scheduled_payment_date, friendly_name, fill = payment_done, size = as.factor(fdn_cat), label = paste0(scales::dollar(scheduled_amount),sep = "\n",  friendly_name, sep = "|", (scheduled_payment_date) )))+
  geom_label(size = 3.5, color = "white")  +
  scale_x_date(limits = as.Date(c('2020-8-30', '2021-08-31')), date_breaks = "month", date_labels = "%b-%y", position =  "bottom") + 
  theme_grey() +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks.y = element_blank()) + 
  theme(axis.title.y = element_blank()) +
   guides(fill = guide_legend(title = "Payment_Done", title.position = "top",
                              
  override.aes = aes(label = ""))) + 
  # scale_fill_discrete(name = "Payment_Done", labels = c("Yes", "No")) +
  scale_fill_viridis_d(name = "Payment_Done", labels = c("Yes", "No"), alpha = 0.8)
  # geom_text_repel() +
  # geom_text(aes(label = scales::dollar(scheduled_amount)))
```

```{r}
# pay_period <- payments_processed %>% 
#   filter(fiscal_year == 2020) %>% 
#   rename(date = scheduled_payment_date) %>% 
#   cross_by_periods(c("month", "quarter", "year")) %>% 
#   summarize(payment = sum(scheduled_amount))
```

```{r}
# pay_period %>%
#   ggplot(aes(date, payment, color = period)) + 
#   geom_line(size = 1, alpha = 0.5) + 
#   scale_y_continuous(labels = dollar_format()) +
#   expand_limits(y = 0)
```

```{r}
# payments_processed %>%
#   drop_na(friendly_name) %>% 
#   mutate(friendly_name = stringr::str_trunc(friendly_name, width = 20, side = "left"))




# %>% 
#     filter(fiscal_year == 2020) %>% 
#   ggplot() +
#   geom_text_repel(aes(x = scheduled_payment_date, y= friendly_name,label = scheduled_amount)) 
#  
  
```

### Next FY Payment Details

```{r}

payments_fy22 <- payments_processed %>%
  filter(fiscal_year == 2022)%>%
  select(
    fiscal_year,
    friendly_name,
    grant_status,
    scheduled_payment_date,
    scheduled_amount,
    actual_payment_date,
    actual_amount
  ) %>%
  arrange(scheduled_payment_date) 
payments_fy22 %>% 
  filter(!grant_status%in%c("New", "In Progress"), 
         !friendly_name %in% c("Fundaula Book Royalty Grant")) %>% 
  
  # knitr::kable()
  flextable::flextable() %>% 
  flextable::border_inner() %>% 
  flextable::border_outer() %>% 
  flextable::colformat_num(j = c(5,7), digits = 0) %>% 
  flextable::colformat_num(j = 1, big.mark = "", digits = 0) %>% 
  flextable:: bold(part = "header")
```

### FY22 Scheduled and Actual Amount

```{r}
payments_fy22 %>%
      summarize(across(c(scheduled_amount, actual_amount), sum, na.rm = TRUE))
```

### Friendly Names

```{r}
payments_processed %>% 
  count(friendly_name)

```

### All Payments related to a particular grant

```{r}
payments_processed %>%
  filter(friendly_name == "WEA 6/ Good Return 1") %>%
  select(
    fiscal_year,
    friendly_name,
    grant_status,
    scheduled_payment_date,
    scheduled_amount,
    actual_payment_date,
    actual_amount
  ) %>%
  arrange(scheduled_payment_date) %>%
  # knitr::kable()
  flextable::flextable() %>% 
  flextable::border_inner() %>% 
  flextable::border_outer() %>% 
  flextable::colformat_num(j = c(5,7), digits = 0) %>% 
  flextable::colformat_num(j = 1, big.mark = "", digits = 0) %>% 
  flextable:: bold(part = "header")
  
```

### New section check for moonreader
