---
title: "Reactable table of GG portfolio"
output:
  html_document:
    rmdformats::robobook
---



```{r , include = FALSE, tidy = TRUE}
library(tidyverse)
library(reactable)
library(lubridate)
library(scales)
options(scipen = 0) # to remove scientific notation of numbers. 
library(DT)

show_in_excel <- function(.data){
  if (interactive()) { # avoid unwanted Excel's executions
    temp <- tempfile(fileext = ".csv") # extension embedded directly
    readr::write_excel_csv(.data, temp) # add BOM for Excel's pleasure
    fs::file_show(temp)
    }
 .data # so that we can continue piping 
}

mtcars %>% 
  show_in_excel() %>% 
  dplyr::select(1:2)
```





## Reactable Grouping and Aggregation
You can group rows in a table by specifying one or more columns in groupBy:

## S2S by Grant Country FY
```{r}
## Reading S2S Actual Data
s2s_actual <-
  readxl::read_xlsx("live_grants.xlsx", sheet = "s2s_actuals") %>%
  janitor::clean_names() %>%
  mutate(report_date = as_date(report_date))


processed_actual <- s2s_actual %>%
  mutate(report_date = ymd(report_date), 
 
    report_month = month(report_date),
    report_year = year(report_date),
    adjustment = ifelse(report_month >= 9, 1, 0),
    report_fiscal = report_year + adjustment,
    report_fiscal = as.factor(report_fiscal)
  ) 

actual <- processed_actual %>% 
  select(contains("total"),benchmark_grant_friendly_name,  report_fiscal,benchmark_beneficiary_country_location )


grant_fy_country_a <- actual %>% 
  group_by(benchmark_grant_friendly_name, report_fiscal, benchmark_beneficiary_country_location) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))





new_names <- c("Grant", "FY", "Country", "Connected_Actual", "Improved_Actual", "Transformed_Actual")

grant_fy_country_a <- grant_fy_country_a %>% 
  set_names(new_names)


# Reading S2S targets data
s2s_target <-
  readxl::read_xlsx("live_grants.xlsx", sheet = "s2s_targets") %>%
  janitor::clean_names() %>%
  mutate(report_date = as_date(report_date))


processed_target <- s2s_target %>%
  mutate(report_date = ymd(report_date), 
 
    report_month = month(report_date),
    report_year = year(report_date),
    adjustment = ifelse(report_month >= 9, 1, 0),
    report_fiscal = report_year + adjustment,
    report_fiscal = as.factor(report_fiscal)
  ) 

target <- processed_target %>% 
  select(contains("total"), benchmark_grant_friendly_name,  report_fiscal,benchmark_beneficiary_country_location )

# target_number_reached:total_target_number_transformed,

grant_fy_country_t <- target %>% 
   group_by(benchmark_grant_friendly_name, report_fiscal, benchmark_beneficiary_country_location) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))


new_names_t <- c("Grant", "FY", "Country", "Connected_t", "Improved_t", "Transformed_t")

grant_fy_country_t <- grant_fy_country_t %>% 
  set_names(new_names_t)

grant_fy_country_t_a <- grant_fy_country_t %>% 
  full_join(grant_fy_country_a, by = c("Grant", "FY", "Country")) # also checked left_join, inner_join yeilds same results


reactable(grant_fy_country_t_a, groupBy = c("Grant", "Country"))
```



## S2S Grant Country Summary FY
```{r}
reactable(
  grant_fy_country_t_a,
  groupBy = c("Grant", "FY"),
  columns = list(
   Country = colDef(aggregate = "unique"),
   Connected_t = colDef(aggregate = "sum", format = colFormat(separators = TRUE)), 
    Improved_t = colDef(aggregate = "sum", format = colFormat(separators = TRUE)),
    Transformed_t = colDef(aggregate = "sum", format = colFormat(separators = TRUE)),
    Connected_Actual = colDef(aggregate = "sum", format = colFormat(separators = TRUE)), 
    Improved_Actual = colDef(aggregate = "sum", format = colFormat(separators = TRUE)),
    Transformed_Actual = colDef(aggregate = "sum", format = colFormat(separators = TRUE))
   ),
  bordered = TRUE
)
```

## S2S per FY per Grant
```{r}
fy_grant_t_a<- grant_fy_country_t_a %>% group_by(FY, Grant) %>% 
            summarise(across(where(is.numeric), sum, na.rm = T))

reactable(fy_grant_t_a,

groupBy = c("FY", "Grant"),
  columns = list(
   Grant = colDef(aggregate = "unique"),
    Connected_t = colDef(aggregate = "sum", format = colFormat(separators = TRUE)), 
    Improved_t = colDef(aggregate = "sum", format = colFormat(separators = TRUE)),
    Transformed_t = colDef(aggregate = "sum", format = colFormat(separators = TRUE)),
    Connected_Actual = colDef(aggregate = "sum", format = colFormat(separators = TRUE)), 
    Improved_Actual = colDef(aggregate = "sum", format = colFormat(separators = TRUE)),
    Transformed_Actual = colDef(aggregate = "sum", format = colFormat(separators = TRUE))
   ),
  bordered = TRUE
)
```

## S2S Grant FY
```{r}
grant_fy_t_a <- grant_fy_country_t_a %>% group_by( Grant, FY) %>% 
            summarise(across(where(is.numeric), sum, na.rm = T))

reactable(grant_fy_t_a, groupBy = c("Grant", "FY"), 
           columns = list(
   FY = colDef(aggregate = "unique"),
   Connected_t = colDef(aggregate = "sum", format = colFormat(separators = TRUE)), 
    Improved_t = colDef(aggregate = "sum", format = colFormat(separators = TRUE)),
    Transformed_t = colDef(aggregate = "sum", format = colFormat(separators = TRUE)),
    Connected_Actual = colDef(aggregate = "sum", format = colFormat(separators = TRUE)), 
    Improved_Actual = colDef(aggregate = "sum", format = colFormat(separators = TRUE)),
    Transformed_Actual = colDef(aggregate = "sum", format = colFormat(separators = TRUE))
   ),
  bordered = TRUE
)
    
 
```

## Agegroup Gender

## Country Gender


## FY Gender

## Grant Gender


## Country FY Gender

## FY Country Gender



## Grant Details to be included
friendly name, funding foundaton, start_date, end_date, grant amount target, grant amount actual

```{r}
gg_grants <-
  readxl::read_excel("live_grants.xlsx", sheet = "all_grants") %>%
  janitor::clean_names() %>%
  mutate(start_date = as_date(start_date),
         end_date = as_date(end_date)) %>%
  # filter(organization_name == "NetHope") %>%
  # show_in_excel()
  select(
    organization_name,
    friendly_name,
    funding_foundation,
    grant_status,
    start_date,
    end_date,
    duration_months,
    target_cash_amount_amount,
    actual_cash_amount_amount,
    impact_location_country,
    impact_location_market_unit,
    sponsoring_location_country,
    sponsoring_location_market_unit
  )
```

```{r}
reactable(gg_grants %>% filter (grant_status != "Closed"))
```


## All grant payments

https://themockup.blog/posts/2020-11-29-bullet-chart-variants-in-r/

https://learnr.wordpress.com/2009/04/23/ggplot2-budget-vs-actual-performance/


## Grant Total and Actual Disbrusement So far
```{r}
payment <-
  readxl::read_excel("live_grants.xlsx", sheet = "payments") %>%
  janitor::clean_names() %>%
  filter(
    type_of_payment == "Cash",
    funding_foundation != "-",
    !grant_status %in% c("New", "In Progress")
  ) %>%
  mutate(
    scheduled_payment_date = lubridate::as_date(scheduled_payment_date),
    actual_payment_date = lubridate::as_date(actual_payment_date)
  ) %>%
  mutate(
    due_date_month_scheduled = month(scheduled_payment_date),
    due_date_year_scheduled = year(scheduled_payment_date),
    adjustment = as.integer(due_date_month_scheduled >= 9),
    fiscal_year_scheduled = due_date_year_scheduled + adjustment,
    due_date_month_actual = month(actual_payment_date),
    due_date_year_actual = year(actual_payment_date),
    adjustment = as.integer(due_date_month_actual >= 9),
    fiscal_year_actual = due_date_year_actual + adjustment
  ) %>% 
select(
    friendly_name, funding_foundation, scheduled_amount_amount, actual_amount_amount, scheduled_payment_date, actual_payment_date, fiscal_year_scheduled, fiscal_year_actual
) %>% 
  arrange(friendly_name)
# Check if any filtered grant by status needs to be included if yes pls revise the filter in the code above
# payment %>% 
#   filter(grant_status %in% c("New", "In Progress")) %>% 
#   count(friendly_name, sort = T)

```

```{r}
payment %>% 
DT::datatable(filter = "top", extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download')
      )
  )
  )
```

### Filter by Grants or a set of Grants
```{r}
payment %>% 
  filter(friendly_name %in% c( "SAVE 5", "SAVE 7 Next Gen", "SAVE 6 Next Gen")) 

```



```{r}
payment_by_grant <- payment%>% 
  group_by(friendly_name) %>% 
  summarize(across(scheduled_amount_amount:actual_amount_amount, .fns = sum, na.rm =T))
  
g <- payment_by_grant %>% 
  pivot_longer(!friendly_name, names_to = "type", 
               values_to = "amount_usd") %>% 
  mutate(friendly_name = fct_reorder(friendly_name, amount_usd)) %>% 
  ggplot(aes( amount_usd, friendly_name, fill = type)) + 
  geom_col(position = "dodge") +
  scale_x_continuous(labels = dollar_format()) +
  theme(legend.position = "none") + 
  labs(x = "Grant amount vs. total payment(USD) YTD", 
       y = " GG grants friendly name", 
       title = "Global Giving live grants", 
       subtitle = "Grant amount vs. total disbrusement YTD")


plotly::ggplotly(g)
  
   

```

## Payment schedule and actual by Grants


```{r}
payment %>% 
  group_by(friendly_name, fiscal_year_scheduled, fiscal_year_actual, scheduled_payment_date, actual_payment_date) %>% 
  summarize(across(scheduled_amount_amount:actual_amount_amount, fns = sum, na.rm = T)) %>% 
  
  select(friendly_name, scheduled_amount_amount, actual_amount_amount, everything()) %>% 
  DT::datatable()
  
```

## Payment Scheduled vs Actual Payment  by Fiscal Year
Use filter by friendly_name, scheduled_payment_date, actual_payment_date etc e.g. to see what is the in year payemnt scheudled and actual for each grant, which are the payments already concluded and most importantly which ones are the upcomig payments. 

```{r}
payment %>% 
  group_by(friendly_name, fiscal_year_scheduled, fiscal_year_actual, scheduled_payment_date, actual_payment_date) %>% 
  summarize(across(scheduled_amount_amount:actual_amount_amount, fns = sum, na.rm = T)) %>% 
    reactable(groupBy = "fiscal_year_scheduled")
  
```


## Payment FY total, per Foundation Total, per Grant Total 
```{r}
reactable(
  payment, 
  groupBy = c( "fiscal_year_scheduled", "funding_foundation", "friendly_name", "scheduled_payment_date", "actual_payment_date", "fiscal_year_actual"),
  columns = list(
    funding_foundation = colDef(aggregate = "unique"),
    # friendly_name = colDef(aggregate = "count"), this step is not useful and since only one option is avaialble better to go for aggregate = uniue which seems quite useful. 
  
   friendly_name = colDef(aggregate = "unique"),
    scheduled_amount_amount = colDef(aggregate = "sum", format = colFormat(separators = TRUE)), 
    actual_amount_amount = colDef(aggregate = "sum", format = colFormat(separators = TRUE))
    
   ),
  bordered = TRUE
)
```



```{r}
reactable(
  payment, 
  groupBy = c( "fiscal_year_scheduled", "funding_foundation", "friendly_name", "scheduled_payment_date", "actual_payment_date", "fiscal_year_actual"),
  columns = list(
    funding_foundation = colDef(aggregate = "unique"),
   scheduled_amount_amount = colDef(aggregate = "sum", format = colFormat(separators = TRUE)), 
    actual_amount_amount = colDef(aggregate = "sum", format = colFormat(separators = TRUE))
    
   ),
  bordered = TRUE
)
```

## Report by Grants

```{r}
reporting <- readxl::read_excel("live_grants.xlsx", sheet = "reporting") %>% janitor::clean_names() %>% 
  filter(!grant_status %in% c("Closed", "In Progress")) %>% 
  
  mutate(due_date = as_date(due_date),
           submission_date = as_date(submission_date),
           stakeholder_call_review_date = as_date(stakeholder_call_review_date)) %>% 
  mutate(due_date_month = month(due_date), 
         submission_date_month = month(submission_date), 
         stakholder_call_review_date_month = month(stakeholder_call_review_date), 
         due_date_year = year(due_date), 
         submission_date_year = year(submission_date), 
         stakeholder_call_review_date_year = year(stakeholder_call_review_date), 
         due_date_adjustment = as.integer(due_date_month >= 9), 
         submission_date_adjustment = as.integer(submission_date_month >=9), 
         stakeholder_call_review_date_adjustment = 
           as.integer(stakholder_call_review_date_month >=9),  
         due_date_fy = due_date_year + due_date_adjustment, 
        submission_date_fy = submission_date_year +  submission_date_adjustment, 
        stakeholder_call_review_date_fy = stakeholder_call_review_date_year + stakeholder_call_review_date_adjustment) %>% 
  
  select(grant_friendly_name,reporting_period, grantee_report_record_type, 	
scope, due_date, submission_date, stakeholder_call_review_date, due_date_fy, submission_date_fy, stakeholder_call_review_date_fy, due_date_month, submission_date_month, stakholder_call_review_date_month)

```

```{r}
reporting %>% 
  count(grant_friendly_name, due_date, due_date_fy, submission_date, submission_date_fy) %>% 
  select(-n) %>% 
  reactable( groupBy = "grant_friendly_name")
             
  
  
```


## Report by Fiscal Year

```{r}
reactable(reporting %>% arrange(due_date), 
             groupBy = "due_date_fy")
 
    # friendly_name = colDef(aggregate = "count"), this step is not useful and since only one option is avaialble better to go for aggregate = uniue which seems quite useful. 
   # 
   # "grant_friendly_name",  "due_date", "submission_date", "submission_date_fy","reporting_period", "reporting_period","stakeholder_call_review_date"),
   
  # bordered = TRUE

```


```{r}
knitr::knit_exit()
```


this is a background work

### Payments where the scheduled date and payment date FYs are different. 
```{r}
payment%>% 
  rowwise() %>% 
  mutate(scheduled_actual_fiscal_diff = 
           fiscal_year_actual - fiscal_year_scheduled) %>% 
  filter(scheduled_actual_fiscal_diff != 0) %>% 
  show_in_excel()
```

### Payments where the scheduled amount and actual amount are different. 

```{r}
payment%>% 
  rowwise() %>% 
  mutate(scheduled_actual_amount_diff = 
           scheduled_amount_amount - actual_amount_amount) %>% 
  filter(scheduled_actual_amount_diff != 0) %>% 
  show_in_excel()
```