---
title: "s2s_actual_permutations_combinations"
author: "Onkar Singh"
date: "9/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(combinat)
library(tidyverse)
```

```{r}
# reference: https://www.r-bloggers.com/2020/09/permutations-in-r/


my_list <- combinat::permn(c("Grant", "FY", "Country", "Gender", "Age_Group", "PwD"))

my_matrix <- do.call(rbind, my_list)
my_matrix <- unique(my_matrix)
dim(my_matrix)
head(my_matrix)
my_matrix
```

### two elements

```{r}
library(gtools)
# reference:https://davetang.org/muse/2013/09/09/combinations-and-permutations-in-r/

dimensions <- c("Grant", "FY", "Country", "Gender", "Age_Group")

# pick any two elements of the dimensions from the 6 elements from the vector

# get all permutations with two elemetns of dimensions

permutations(n = 5, r = 2, v = dimensions) %>% 
  as_tibble() %>% 
    arrange(V1)
```

### three elements

```{r}
# get all permutations with three  elemetns of dimensions

permutations(n = 5, r = 3, v = dimensions) %>% 
  as_tibble() %>% 
    arrange(V1)
```



### four elements

```{r}
# get all permutations with four  elemetns of dimensions

permutations(n = 5, r = 4, v = dimensions)%>% 
  as_tibble() %>% 
    arrange(V1)

```

### five elements
```{r}
# get all permutations with five  elements of dimensions

permutations(n = 5, r = 5, v = dimensions)%>% 
  as_tibble() %>% 
    arrange(V1)

```



## permutation with replacements

### two elements with replacement
```{r}
library(gtools)
# reference:https://davetang.org/muse/2013/09/09/combinations-and-permutations-in-r/

dimensions <- c("Grant", "FY", "Country", "Gender", "Age_Group")

# pick any two elements of the dimensions from the 6 elements from the vector

# get all permutations with two elemetns of dimensions with replacement

permutations(n = 5, r = 2, v = dimensions, repeats.allowed=T)
```


### five elements with replacements
```{r}
five_elements <- permutations(n = 5, r = 5, v = dimensions, repeats.allowed=T)

dim(five_elements)
```






### Reference


```{r}
library(dplyr)
library(janitor)
library(lubridate)
library(validate)
```


# Reading data from updated excel

```{r}
s2s_actual <- readxl::read_xlsx("live_grants.xlsx", sheet = "s2s_actuals") %>% 
  clean_names() %>% 
  mutate(report_date = as_date(report_date))
```


## Processing 1: creating report fiscal column
```{r}
processed_actual <- s2s_actual %>%
  mutate(report_date = ymd(report_date), 
 
    report_month = month(report_date),
    report_year = year(report_date),
    adjustment = ifelse(report_month >= 9, 1, 0),
    report_fiscal = report_year + adjustment,
    report_fiscal = as.factor(report_fiscal)
  ) 

```

### S2S total across all grants
```{r}
processed_actual %>% 
  group_by(benchmark_grant_friendly_name) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))
```





### S2S per FY Summary all actual metrics


```{r}
processed_actual %>% 
  select(-actual_percent_pw_d:-adjustment) %>% 
  group_by(report_fiscal) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))
```

### CIT Summary per FY

```{r}
processed_actual %>% 
  select(contains("total"), report_fiscal) %>% 
  group_by(report_fiscal) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))
```

### CIT total actual per grant

```{r}
cit_actual_grant <- processed_actual %>% 
  select(contains("total"), benchmark_grant_friendly_name) %>% 
  group_by(benchmark_grant_friendly_name) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))
cit_actual_grant
```

### CIT actual per grant per FY

```{r}
cit_actual_grant_fy <- processed_actual %>% 
  select(contains("total"), benchmark_grant_friendly_name, report_fiscal) %>% 
  group_by(benchmark_grant_friendly_name, report_fiscal) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))
cit_actual_grant_fy 
```

CIT actual per grant per FY per country

```{r}
cit_actual_grant_fy_country <- processed_actual %>% 
  select(contains("total"), benchmark_grant_friendly_name, report_fiscal, benchmark_beneficiary_country_location) %>% 
  group_by(benchmark_grant_friendly_name, report_fiscal, benchmark_beneficiary_country_location) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))
cit_actual_grant_fy_country 
```



### CIT total actual per country

```{r}
cit_actual_country <- processed_actual %>% 
  select(contains("total"), benchmark_beneficiary_country_location) %>% 
  group_by(benchmark_beneficiary_country_location) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))
cit_actual_country
```


### CIT actual per country per FY

```{r}
cit_actual_country_fy <- processed_actual %>% 
  select(contains("total"), benchmark_beneficiary_country_location, report_fiscal) %>% 
  group_by(benchmark_beneficiary_country_location, report_fiscal) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))

cit_actual_country_fy
```


### CIT actual per country per FY per grant

```{r}
cit_actual_country_fy_grant <- processed_actual %>% 
    select(contains("total"), benchmark_beneficiary_country_location, report_fiscal, benchmark_grant_friendly_name) %>% 
  group_by(benchmark_beneficiary_country_location, report_fiscal, benchmark_grant_friendly_name) %>% 
  summarise(across(where(is.numeric), sum, na.rm = T))

cit_actual_country_grant
```


[Calculate Combinations and Permutations in R](https://www.geeksforgeeks.org/calculate-combinations-and-permutations-in-r/)

```{r}
library(combinat)
two_elem <- combn(dimensions[1:6], 2)
two_elem 
```

```{r}
three_elem <- combn(dimensions[1:6], 3)
three_elem
```

```{r}
four_elem <- combn(dimensions[1:6], 4)
four_elem
```


```{r}
five_elem <- combn(dimensions[1:6], 5)
five_elem
```

```{r}
six_elem <- combn(dimensions[1:6], 6)
six_elem
```



## Data Validation Rules

### CIT Rules
Connected total for all grants are sum total of all Connected level metrics. 

Improved total for each grants are sum total of all improved metrics

Transformed  total for each grant is sum totla of all Transformed metrics 

### CIT Gender Rules
Connected male of a grant   is greater than or equal to  Connected male of Improved
Connected female of a grant  is greater than or equal to Connected female of Improved
Connected other gender category of a grant is greater than or equal to the connected other gender of the Improved level

Improved male of a grant   is greater than or equal to   male of Trasnformed
Improved female of a grant  is greater than or equal to  female of Transformed
Improved other gender category of a grant is greater than or equal to the other gender of the Transformed level

Connected total is the sum total total of all gender figures at the Connected level

Improved total is the sume totlal of all gender figures at the Improved level
Transformed total is the sume total of all gender at the Tranformed level


### CIT Age Group Rules

Connected total is the sum totla of all age group figures at the Connected level

Improved  total is the sum totla of all age group figures at the Improved level

Transformed total is the sum totla of all age group figures at the transformed level


### CIT Grants Rules
Connected figures for all grants are greater than or equal to improved figures. Improved figures for all grants are greater than or equal to the Transformed figures

At the grant level, 

the Connected figures are greater than or equal to the Improved figures
The Improved figures are greater than or equal to the Tranformed level
The Connected male figures are great than or equal to the Improved males figures 
The Connected female figures are great than or equal to the Improved females figures 
The Connected other gender category  figures are great than or equal to the Improved other gender figures 

The Improved male figures are greater than or equal to the Tranformed male level

The Improved female figures are greater than or equal to the Tranformed level

The Improved other gender figures are greater than or equal to the other gender figures Tranformed level


The Connected child  figures are greater than or equal to the Improved child figures 
The Connected youth figures are great than or equal to the Improved youth figures 
The Connected adult figures are great than or equal to the Improved adult figures 
The Connected unknown demographics figures are great than or equal to the unknown demographics youth figures 



### CIT FY Rules
for the FY level check if 
the Connected figures are greater than or equal to the Improved figures
The Improved figures are greater than or equal to the Tranformed level
The Connected male figures are great than or equal to the Improved males figures 
The Connected female figures are great than or equal to the Improved females figures 
The Connected other gender category  figures are great than or equal to the Improved other gender figures 

The Improved male figures are greater than or equal to the Tranformed male level

The Improved female figures are greater than or equal to the Tranformed level

The Improved other gender figures are greater than or equal to the other gender figures Tranformed level


The Connected child  figures are greater than or equal to the Improved child figures 
The Connected youth figures are great than or equal to the Improved youth figures 
The Connected adult figures are great than or equal to the Improved adult figures 
The Connected unknown demographics figures are great than or equal to the unknown demographics youth figures 


### CIT Country Rules
At the country level, 
the Connected figures are greater than or equal to the Improved figures
The Improved figures are greater than or equal to the Tranformed level
The Connected male figures are great than or equal to the Improved males figures 
The Connected female figures are great than or equal to the Improved females figures 
The Connected other gender category  figures are great than or equal to the Improved other gender figures 

The Improved male figures are greater than or equal to the Tranformed male level

The Improved female figures are greater than or equal to the Tranformed level

The Improved other gender figures are greater than or equal to the other gender figures Tranformed level


The Connected child  figures are greater than or equal to the Improved child figures 
The Connected youth figures are great than or equal to the Improved youth figures 
The Connected adult figures are great than or equal to the Improved adult figures 
The Connected unknown demographics figures are great than or equal to the unknown demographics youth figures 

### CIT Country FY Rules




### CIT metrics Rules

### CIT metrics gender rules




