---
title: 'Skills to Succeed Targets and Actuals'
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, 
  message = FALSE, 
  echo = FALSE)
  
```

```{r}
# load tidyverse for the data manipulation and visualization
library(tidyverse)
# load the Janitor for Clearning up the variable names
library(janitor)
library(lubridate) # for date and times
library(readxl)
library(writexl)

library(knitr) # for making html tables neat using kable(table) function
# library(xaringan) # to launch infinite_moonreader function for auto update
library(DT)
```

## global_giving_grant_metrics_s2s_all

[global_giving_grant_metrics_s2s_all](https://impactaccenture.lightning.force.com/lightning/r/Report/00O1I000007CYSJUA4/view?fv1=0061I000007Uc0m)

```{r results = FALSE}

# all_s2s <- read_csv("global_giving_grant_metrics_s2s_all.csv") %>%
#   clean_names() %>% 
#   mutate(across(is.logical, as.double))
#  
# 
# glimpse(all_s2s) 
# all_s2s



```

### data processed

```{r data_processed, results = FALSE}
processed <- all_s2s %>%
  mutate(report_date = mdy(report_date), 
 
    report_month = month(report_date),
    report_year = year(report_date),
    adjustment = ifelse(report_month >= 9, 1, 0),
    report_fiscal = report_year + adjustment,
    report_fiscal = as.factor(report_fiscal)
  ) %>% 
 pivot_longer(
    cols = actual_number_connected_adult:total_target_number_transformed ,
    names_to = "metric",
    values_to = "s2s",
    values_drop_na = TRUE
  ) %>%
  mutate(
    metric = as.factor(metric))


# %>%
#   mutate(
#     metric_summary = case_when(
#       metric == "target_number_reached" ~ "Connected",
#       metric == "target_number_skilled" ~ "Improved",
#       metric == "target_number_obtained_work_experience" ~ "Improved",
#       metric == "target_number_improved_mindset" ~ "Improved",
#       metric == "target_number_improved_career_management" ~ "Improved",
#       metric == "target_number_re_entered_formal_education" ~ "Transformed",
#       metric == "target_number_increased_career_resilience" ~ "Transformed",
#       metric == "target_number_increased_income"   ~ "Transformed",
#       metric == "target_number_employed"   ~ "Transformed",
#       metric == "target_number_self_employed"     ~ "Transformed",
#       metric == "target_number_started_a_business"   ~ "Transformed",
#       metric == "target_number_grew_a_business"     ~ "Transformed",
#       TRUE ~ "Other"
#     )
#   )  



# %>% 
#   mutate(metric = as.character(metric)) %>% 
#   separate(metric, c("a", "b"), extra = "merge") %>% 
#   filter(!grepl('target', b)) %>% 
#   mutate(across(is.character, as.factor)) %>% 
#   rename(metric = b)


  
  
```

### All metric list

```{r all_metrics_list, results = FALSE}
levels(processed$metric)
```

### CIT target and actual for all grants

```{r}
cit_target_actual <- processed %>% 
  # filter(report_fiscal%in% 2010:2020) %>% # to make it comment out this filter line
  filter(str_detect(metric, "total")) %>% 
  group_by(grant_friendly_name, metric) %>% 
  summarize(total_s2s = sum(s2s)) %>% 
  pivot_wider(names_from = metric, values_from = total_s2s) %>%  
  select(grant_friendly_name, total_target_number_connected, total_target_number_improved, total_target_number_transformed, everything()) 


cit_target_actual%>% 
DT::datatable(filter = "top", extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download')
      )
  )
  )

```

filter connected targeted for live grants for data check or update

```{r}
friendly_names_filter <- c("ACCES 2", "AMF/DQI/DQL FP", "Article 1_Jobready FP", "Article 1 Grant 2", "Aspen 1", "EfE 3", "FE 6 Single Step", "Foundation Forge - RC 3", "Fundacion ProEmpleo RC 3", "Fundaula Book Royalty Grant", "Goodwill 1", "JA 3", "Minuto de Dios - RC 3", "Norwegian Foundation Research", "Plan 6", "PLAN 8 Strategic Extension", "Rede Cidada - RC 3", "SAVE 5", "SAVE 6 Next Gen", "SAVE 7 Next Gen", "WEA 6/ Good Return 1", "YBI 5", "YBI 6 - YBI Strategic Extension", "LCD 5", "SAVE 8", "UNHCR GG Grant", "FE 5 Next Gen", "FY19  LC Success Coaching - Global", "LCD 4", "PLAN 7 Next Gen", "Human + Machine Book Royalty Grant", "AOGF", "UKOGF")

cit_target_actual %>% 
  filter(grant_friendly_name %in% friendly_names_filter) %>% 
  select(grant_friendly_name, total_target_number_connected) 

# datapasta::tribble_paste()
# tibble::tribble(
#                      ~grant_friendly_name, ~total_target_number_connected,
#                                 "ACCES 2",                          40800,
#                          "AMF/DQI/DQL FP",                         150000,
#                       "Article 1 Grant 2",                         101003,
#                   "Article 1_Jobready FP",                           5000,
#                                 "Aspen 1",                         194700,
#                                   "EfE 3",                          65762,
#                           "FE 5 Next Gen",                           2350,
#                        "FE 6 Single Step",                          19500,
#             "Fundaula Book Royalty Grant",                           2250,
#      "FY19  LC Success Coaching - Global",                             20,
#                              "Goodwill 1",                          30050,
#                                    "JA 3",                        2338246,
#                                  "Plan 6",                          21444,
#                         "PLAN 7 Next Gen",                            360,
#              "PLAN 8 Strategic Extension",                           8100,
#                      "Rede Cidada - RC 3",                           9234,
#                                  "SAVE 5",                          57926,
#                         "SAVE 6 Next Gen",                            200,
#                         "SAVE 7 Next Gen",                         334264,
#                    "WEA 6/ Good Return 1",                          37000,
#                                   "YBI 5",                         190000,
#         "YBI 6 - YBI Strategic Extension",                          77103
#      )
```

### CIT FY target and actual for all grants

```{r}
processed %>% 
  # filter(report_fiscal%in% 2010:2020) %>% # to make it comment out this filter line
   filter(str_detect(metric, "total")) %>% 
  group_by(grant_friendly_name, report_fiscal, metric) %>% 
  summarize(total_s2s = sum(s2s)) %>% 
  pivot_wider(names_from = metric, values_from = total_s2s) %>% 
  select(grant_friendly_name, report_fiscal, total_target_number_connected, total_target_number_improved, total_target_number_transformed, everything()
         ) %>% 
  DT::datatable(filter = "top", extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download')
      )
  )
  )
  

```

### CIT Country target and actual for all grants

```{r}
processed %>% 
  # filter(report_fiscal%in% 2010:2020) %>% # to make it comment out this filter line
  filter(str_detect(metric, "total")) %>% 
    group_by(grant_friendly_name, beneficiary_country, metric) %>% 
  summarize(total_s2s = sum(s2s)) %>% 
  pivot_wider(names_from = metric, values_from = total_s2s) %>% 
  select(grant_friendly_name, beneficiary_country, total_target_number_connected, total_target_number_improved, total_target_number_transformed, everything()) %>% 
  DT::datatable(filter = "top", extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download')
      )
  )
  )
```

### CIT Country FY target and actual for all grants

```{r}
processed %>% 
  # filter(report_fiscal%in% 2010:2020) %>% # to make it comment out this filter line
  filter(str_detect(metric, "total")) %>% 
    group_by(grant_friendly_name, beneficiary_country, report_fiscal, metric) %>% 
  summarize(total_s2s = sum(s2s)) %>% 
  pivot_wider(names_from = metric, values_from = total_s2s) %>% 
  select(grant_friendly_name, beneficiary_country, report_fiscal, total_target_number_connected, total_target_number_improved, total_target_number_transformed, everything()) %>% 
  DT::datatable(filter = "top", extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download')
      )
  )
  )
```

### CIT target and actual per grant/ per organization

```{r results = FALSE}
cit <- processed %>% 
  # filter(report_fiscal%in% 2010:2020) %>% # to make it comment out this filter line
  filter(str_detect(metric, "total")) %>% 
  filter(str_detect(grant_friendly_name, "PLAN|Plan")) %>% 
  group_by(grant_friendly_name, metric) %>% 
  summarize(total_s2s = sum(s2s)) %>% 
  pivot_wider(names_from = metric, values_from = total_s2s)
  
```

### CIT per Country target and actual per organization

```{r results = FALSE}
processed %>% 
  # filter(report_fiscal%in% 2010:2020) %>% # to make it comment out this filter line
  filter(str_detect(metric, "total")) %>% 
  filter(str_detect(grant_friendly_name, "PLAN|Plan")) %>% 
  group_by(grant_friendly_name, beneficiary_country, metric) %>% 
  summarize(total_s2s = sum(s2s)) %>% 
  pivot_wider(names_from = metric, values_from = total_s2s)
```

### CIT FY10:FY20 target and actual per FY per country per grant/ per organization

```{r results = FALSE}
processed %>% 
  filter(report_fiscal%in% 2010:2022) %>% # to make it comment out this filter line
  filter(str_detect(metric, "total")) %>% 
  filter(str_detect(grant_friendly_name, "ACCES")) %>% 
  group_by(grant_friendly_name, report_fiscal, beneficiary_country, metric) %>% 
  summarize(total_s2s = sum(s2s)) %>% 
  pivot_wider(names_from = metric, values_from = total_s2s) %>% 
  filter(grant_friendly_name == "ACCES 2")

```

### FRIENDLY NAME

```{r friendly_name,  results = FALSE}
processed$grant_friendly_name %>% 
  unique()

```

```{r}
cit_metrics <- c("total_actual_number_connected", "total_target_number_connected", "total_actual_number_improved", "total_target_number_improved", "total_actual_number_transformed", "total_target_number_transformed" )

cit_details <- c(
  "actual_number_reached",
  "actual_number_skilled",
  "actual_number_employed",
  "actual_number_employed_by_accenture",
  "actual_number_grew_a_business",
  "actual_number_obtained_work_experience",
  "actual_number_re_entered_formal_education",
  "actual_number_started_a_business",
  "target_number_reached",
   "target_number_skilled",
  "target_number_employed",
  "target_number_employed_by_accenture",
  "target_number_grew_a_business",
  "target_number_improved_career_management",
  "target_number_improved_mindset",
  "target_number_increased_career_resilience",
  "target_number_obtained_work_experience",
  "target_number_re_entered_formal_education",
  "target_number_self_employed",
  "target_number_started_a_business")

gender_metrics <- c("actual_number_connected_adult",
  "actual_number_connected_child",
  "actual_number_connected_female",
  "actual_number_connected_male",
  "actual_number_connected_non_binary",
  "actual_number_connected_prefer_not_to_answer",
  "actual_number_connected_unknown_other",
  "actual_number_connected_youth",
  "actual_number_employed",
  "actual_number_employed_by_accenture",
  "actual_number_grew_a_business",
  "actual_number_obtained_work_experience",
  "actual_number_re_entered_formal_education",
  "actual_number_reached",
  "actual_number_skilled",
  "actual_number_started_a_business",
  "target_number_employed",
  "target_number_employed_by_accenture",
  "target_number_grew_a_business",
  "target_number_improved_career_management",
  "target_number_improved_mindset",
  "target_number_increased_career_resilience",
  "target_number_obtained_work_experience",
  "target_number_re_entered_formal_education",
  "target_number_reached",
  "target_number_self_employed",
  "target_number_skilled",
  "target_number_started_a_business")

adult_child_youth <- c("actual_number_connected_adult",
  "actual_number_connected_child",
  "actual_number_connected_female",
  "actual_number_connected_male",
  "actual_number_connected_non_binary",
  "actual_number_connected_prefer_not_to_answer",
  "actual_number_connected_unknown_other",
  "actual_number_connected_youth",
  "actual_number_employed",
  "actual_number_employed_by_accenture",
  "actual_number_grew_a_business",
  "actual_number_obtained_work_experience",
  "actual_number_re_entered_formal_education",
  "actual_number_reached",
  "actual_number_skilled",
  "actual_number_started_a_business",
  "target_number_employed",
  "target_number_employed_by_accenture",
  "target_number_grew_a_business",
  "target_number_improved_career_management",
  "target_number_improved_mindset",
  "target_number_increased_career_resilience",
  "target_number_obtained_work_experience",
  "target_number_re_entered_formal_education",
  "target_number_reached",
  "target_number_self_employed",
  "target_number_skilled",
  "target_number_started_a_business")




non_cit_metrics <- processed %>% 
  # filter(report_fiscal%in% 2010:2020) %>% # to make it comment out this filter line
  filter(metric %in% cit_details) %>% 
  mutate(metric_calc = case_when(
   metric ==  "target_number_employed" ~ "target_transformed", 
 metric == "target_number_employed_by_accenture" ~ "target_transformed_subset", 
  metric == "target_number_grew_a_business" ~ "target_transformed",
  metric == "target_number_improved_career_management" ~ "target_improved" ,
  metric == "target_number_improved_mindset" ~ "target_improved", 
  metric == "target_number_increased_career_resilience" ~ "target_transformed",
 metric ==  "target_number_obtained_work_experience" ~ "target_improved",
 metric == "target_number_re_entered_formal_education" ~  "target_transformed",
 metric == "target_number_reached" ~ "target_connected",
  metric == "target_number_self_employed" ~ "target_transformed",
 metric ==  "target_number_skilled" ~ "target_improved",
  metric == "target_number_started_a_business" ~ "target_transformed",
 metric == "actual_number_reached"                     ~ "actual_connected"   ,
 metric ==  "actual_number_skilled" ~ "actual_improved",
 metric ==  "actual_number_employed" ~ "actual_transformed",
 metric ==  "actual_number_employed_by_accenture" ~ "actual_transformed_subset",
 metric ==  "actual_number_grew_a_business" ~ "actual_transformed",
 metric ==  "actual_number_obtained_work_experience" ~ "actual_improved",
 metric ==  "actual_number_re_entered_formal_education" ~ "actual_transformed",
 metric ==  "actual_number_started_a_business" ~ "actual_transformed",
 
  TRUE ~ "other" ))
 
  
 non_cit_metrics %>% 
  count(metric_calc, metric, sort = T)
 
 
    # DataEditR::data_edit(x = non_cit_metrics_count )


```

### S2S_Targets_2025

[2025_All Grants_Any Status S2S Targets](https://impactaccenture.lightning.force.com/lightning/r/Report/00O1I000006hYmhUAE/view?queryScope=userFolders)

\#\#\#S2S_Actuals_2025

[All Grant S2S Report_Actuals_2025](https://impactaccenture.lightning.force.com/lightning/r/Report/00O1I000007CmwJUAS/view?queryScope=userFolders)

\#\#\#REFERENCE ONLY
